Faithful Variable Screening for\\ High-Dimensional Convex Regression

### 2015-12-07 tex/scam/sparsistency.tex
mods for supplement

This result holds regardless of whether or not we impose the
boundedness conditions in optimization~\eqref{opt:alternate_opt}
and~\eqref{opt:alternate_opt_concave}.  The full proof of
Theorem~\ref{thm:deterministic} is in
Section~\ref{sec:deterministic_proof} of the Appendix. We allow $S$ in
Theorem~\ref{thm:deterministic} to be any set containing the relevant
variables; in Lasso analysis, $S$ is taken to be the set of relevant
variables; we will take $S$ to be the set of variables chosen by the
additive convex and decoupled concave procedure in the population
setting, which is guaranteed to contain the relevant variables because
of additive faithfulness.

@@

The details of the proof are given in
Section~\ref{sec:deterministic_proof} of the Appendix.

@@

The proof of Theorem~\ref{thm:false_positive} exploits independence of
$\hat{r}$ and $X_k$ under assumption A1; when $\hat{r}$ and $X_k$ are independent,
$\hat{r}^\tran \mathbf{1}_{(i':n)}$ is the sum of $n - i' +1$ random
coordinates of $\hat{r}$.  We can then use concentration of
measure results for sampling without replacement to argue that $|
\frac{1}{n} \hat{r}^\tran\mathbf{1}_{(i':n)}|$ is small with high
probability. The result of Theorem~\ref{thm:deterministic} is then
used. The full proof of Theorem~\ref{thm:false_positive} is in
Section~\ref{sec:false_positive_proof} of the Appendix.

@@

This is a finite sample version of
Theorem~\ref{thm:convex_faithful}. We need stronger assumptions in
Theorem~\ref{thm:false_negative} to use our additive faithfulness
result, Theorem~\ref{thm:convex_faithful}. The full proof of Theorem~\ref{thm:false_negative} is in Section~\ref{sec:false_negative_proof} of the appendix.

>>>>

This result holds regardless of whether or not we impose the
boundedness conditions in optimization~\eqref{opt:alternate_opt}
and~\eqref{opt:alternate_opt_concave}.  The full proof of
Theorem~\ref{thm:deterministic} is in
Section~\ref{sec:deterministic_proof} of the supplementary material \citep{supplement}. We allow $S$ in
Theorem~\ref{thm:deterministic} to be any set containing the relevant
variables; in Lasso analysis, $S$ is taken to be the set of relevant
variables; we will take $S$ to be the set of variables chosen by the
additive convex and decoupled concave procedure in the population
setting, which is guaranteed to contain the relevant variables because
of additive faithfulness.

@@

The details of the proof are given in
Section~\ref{sec:deterministic_proof} of the supplementary material \citep{supplement}.

@@

The proof of Theorem~\ref{thm:false_positive} exploits independence of
$\hat{r}$ and $X_k$ under assumption A1; when $\hat{r}$ and $X_k$ are independent,
$\hat{r}^\tran \mathbf{1}_{(i':n)}$ is the sum of $n - i' +1$ random
coordinates of $\hat{r}$.  We can then use concentration of
measure results for sampling without replacement to argue that $|
\frac{1}{n} \hat{r}^\tran\mathbf{1}_{(i':n)}|$ is small with high
probability. The result of Theorem~\ref{thm:deterministic} is then
used. The full proof of Theorem~\ref{thm:false_positive} is in
Section~\ref{sec:false_positive_proof} of the supplementary material \citep{supplement}.

@@

This is a finite sample version of
Theorem~\ref{thm:convex_faithful}. We need stronger assumptions in
Theorem~\ref{thm:false_negative} to use our additive faithfulness
result, Theorem~\ref{thm:convex_faithful}. The full proof of
Theorem~\ref{thm:false_negative} is in
Section~\ref{sec:false_negative_proof} of the supplement \citep{supplement}.

### 2015-12-07 tex/scam/supplement.tex
mods for supplement

\section{Supplement:  Proofs of Technical Results}

@@

We restate Theorem~\ref{thm:deterministic} first for convenience. 
The following holds regardless of whether we impose the $B$-boundedness condition (see discussion at the beginning of Section~\ref{sec:finitesample} for definition of the $B$-boundedness condition).

@@

>>>>

\documentclass[12pt,pdftex,aos,noinfoline,addressasfootnote]{imsart}
%\documentclass[12pt,pdftex,generic,noinfoline]{imsart}

\RequirePackage[OT1]{fontenc}
\usepackage{amsthm,amsmath,amsfonts,natbib,mathtools,custom_math,amssymb}
\RequirePackage{hypernat}
\usepackage[ruled,section]{algorithm}
\usepackage[noend]{algorithmic}
\usepackage{graphicx}
%\usepackage[hscale=0.7,vscale=0.8]{geometry}
\usepackage[text={6.0in,8.6in},centering]{geometry}
\usepackage{subfigure}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{yhmath}
\usepackage[usenames,dvipsnames]{xcolor}
\definecolor{shadecolor}{gray}{0.9}
\definecolor{shadecolor}{gray}{0.9}
\hypersetup{citecolor=MidnightBlue}
\hypersetup{linkcolor=MidnightBlue}
\hypersetup{urlcolor=MidnightBlue}
\usepackage{enumerate}
\usepackage{multirow}
\usepackage{xr}
\externaldocument{main}

\renewcommand{\baselinestretch}{1.00}
%\parskip12pt
%\parindent0pt
\setcounter{tocdepth}{2}

\input{macros}
\begin{document}

\begin{supplement}
%\sname{Supplement A}
\stitle{Supplement to Faithful Variable Screening for High-Dimensional Convex Regression}
\slink[doi]{doi}
\sdatatype{.pdf}
\sdescription{We provide detailed proofs of certain technical results,
together with further explanation of the Gaussian example
and simplifications when the density is a product.}
\end{supplement}

\section{Proofs of Technical Results}

@@

We restate Theorem~\ref{thm:deterministic} first for convenience. 
The following holds regardless of whether we impose the
$B$-boundedness condition  $\|f_k^*\|_\infty \leq B$
used in the consistency analysis.

@@

\bibliographystyle{imsart-nameyear}
\bibliography{local}

\end{document}
